Tempus: Probabilistic Network Latency Verifier

### 2022-11-29 paper/main.tex
[Paper] minor update to points

\begin{itemize}
    \item While the amount of convolution gave us a pretty good proxy for performance, we could see 
        that there's still some variations
    \item This is due to the fact that we used two kinds of convolutions: analytical and numerical.
    \item Since numerical convolution is slower, we could see that for the same topology and the same amount of 
        overall convolution, \textbf{more numerical convolution will result in longer runtime performance}.
    \item In the worst case (all numerical), the grouping optimization would have no effect
\end{itemize}

@@

\section{Conclusion}
\begin{itemize}
    \item Tempus is a scalable latency SLA verifier. It could probabilistically verify in the order of minutes
    \item Consolidation and memoization is an effective optimization strategy, although the exact magnitude of 
        its effectiveness will depend on the network topology, specifically on the amount of paths and their 
        length.
    \item The grouping optimization strategy is effective only if most distributions in the network can be 
        convolved analytically. In the worst case, if most of them can't (like LogNormal only) then this 
        optimization would have no improvement.
\end{itemize}

>>>>

\begin{itemize}
    \item While the amount of convolution gave us a pretty good proxy for performance, we could see 
        that there's still some variations
    \item This is due to the fact that we used two kinds of convolutions: analytical and numerical.
    \item Since numerical convolution is slower, we could see that for the same topology and the same amount of 
        overall convolution, \textbf{more numerical convolution will result in longer runtime performance}.
\end{itemize}

@@

\section{Conclusion}
\begin{itemize}
    \item Tempus is a scalable latency SLA verifier. It could probabilistically verify in the order of minutes
    \item Consolidation and memoization is an effective optimization strategy, although the exact magnitude of 
        its effectiveness will depend on the network topology, specifically on the amount of paths and their 
        length.
    \item The grouping optimization strategy is an effective optimization strategy, although the exact magnitude 
        of its effectiveness will depend on the amount of similar distributions that can be convolved analytically
\end{itemize}
